A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-24 text/manuscript.Rmd
Update fig3 with sankey plot, remove oncoprint in fig5

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE)
suppressPackageStartupMessages(c(
  library(rstan),
  library(foreach),
  library(sqldf),
  library(tidyverse),
  library(ggthemes),
  library(data.table),
  library(biomaRt),
  library(dplyr),
  library(GenomicRanges),
  library(SummarizedExperiment),
  library(reactome.db),
  library(plyr),
  library(cluster),
  library(pheatmap),
  library(clusterProfiler),
  library(org.Hs.eg.db),
  library(dbscan),
  library(class),
  library(TCGAbiolinks),
  library(patchwork),
  library(ggplotify),
  library(ComplexHeatmap),
  library(knitr),
  library(kableExtra),
  library(UpSetR),
  library(cowplot),
  library(doRNG),
  library(uwot),
  library(janitor),
  library(FactoMineR),
  library(seriation),
  library(rtracklayer),
  library(poibin),
  library(flextable),
  library(plot3D),
  library(ggfortify),
  library(maftools),
  library(survival),
  library(ggalluvial)
))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE)
suppressPackageStartupMessages(c(
  library(rstan),
  library(foreach),
  library(sqldf),
  library(tidyverse),
  library(ggthemes),
  library(data.table),
  library(biomaRt),
  library(dplyr),
  library(GenomicRanges),
  library(SummarizedExperiment),
  library(reactome.db),
  library(plyr),
  library(cluster),
  library(pheatmap),
  library(clusterProfiler),
  library(org.Hs.eg.db),
  library(dbscan),
  library(class),
  library(TCGAbiolinks),
  library(patchwork),
  library(ggplotify),
  library(ComplexHeatmap),
  library(knitr),
  library(kableExtra),
  library(UpSetR),
  library(cowplot),
  library(doRNG),
  library(uwot),
  library(janitor),
  library(FactoMineR),
  library(seriation),
  library(rtracklayer),
  library(poibin),
  library(flextable),
  library(plot3D),
  library(ggfortify),
  library(maftools),
  library(survival),
  library(ggalluvial),
  library(grid),
  library(gridBase)
))
```
